Scattering of massless particles: scalars, gluons and gravitons

### 2024-07-23 test/main.tex
New

\section{CHY Formula}
\begin{frame}
    \frametitle{Motivation}
    %Most of the developments of amplitudes before have made for some specific theories, like N=4 super yang-mills theory and N=8 supergravity.
    %The natural question is that what is the space of all field theories whose tree level S-matrix can be expressed in a compact form? 
    \begin{itemize}
        \item Compact form of amplitudes for sclar, pure Yang-Mills and gravity theories in any spacetime dimension.
        %The author introduce a compact form of tree level amplitudes for three different theories, colored scalar theory, pure Yang-Mills and Einstein gravity.
        %The concrete form of this formula implies that there is a relation between these three theories, and it may give some new insights of the connection between gravity and gauge theory.
        \item A special amplitude --- Double partial amplitude
        %Because of the special color structure of this scalar theory, the authors proposed a easy method to compute all scalar tree amplitudes, and then pure Yang-Mills and gravity can also be done using similar methods.
        \item BCJ double copy at tree level
        %In terms of this construction of amplitudes, it is easy to obtain the BCJ double copy relation.
        \item Related to other theories, such as EYM, EM, NLSM and so on.
        %In the following paper of these authors, by introducing some special operations which performed on the integrand of CHY formula, they give some relations between other theories.   
        \item One-loop corrections to scattering amplitudes of scalars and gauge bosons can be obtained from tree amplitudes in one higher dimension. 
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{Scattering equations}
    % In the Witten-RSV formulation, tree-level field theory amplitudes are given as integrals that localize on generic spheres.
    It has been proposed that there is connection between the scattering data of n massless particles and the n-punctured sphere from a rational map
    \begin{equation*}
        k_\mu^a=\frac{1}{2\pi i}\oint_{|z-\sigma_a|}dz\frac{p^\mu(z)}{\prod ^n_{b=1}(z-\sigma_b)}
    \end{equation*}

    To discribe the n-punctured sphere more properly, we can introduce the Riemann sphere as
    \begin{equation*}
        \mathbb{CP}^1\cong \mathcal{S}^2\cong \mathbb{C}\cup\{\infty\}
    \end{equation*}
    each $\sigma_a$ represents a puncture located in the Riemann sphere.

@@

    %\begin{itemize}
    %    \item Third step, we can read off the corresponding amplitudes from the equivalent Feynman diagram. 
    %\end{itemize}
    %\begin{itemize}
    %\item First step, determine the orientation of the disk by ordering $\alpha$, and define the loop segments by ordering $\beta$, which also determine the orientation of every polygon.
    %    \item Second step, (1) each polygon with odd number vertices contributes a plus sign if the orientation is the same as disk, and a minus sign oppositely;
    %          (2) each polygon with even number vertices contribute a minus sign; (3) each intersection point contributes a minus sign.
    %\end{itemize}
    \begin{figure}
        \centering
        \includegraphics[width=1\linewidth]{6.png}
    \end{figure}
    The final answer is that
    \begin{equation*}
        m_8^{(0)}(I|54376218)=(-1)^6\left(\frac{1}{s_{21}}+\frac{1}{s_{18}}\right)\left(\frac{1}{s_{34}}+\frac{1}{s_{45}}\right)\frac{1}{s_{345}s_{812}s_{67}}
    \end{equation*}
\end{frame}
\begin{frame}
    Now we can unify the color factor and kinematic factor as e in all three theories, so the full amplitude can be written in a unified form
    \begin{equation*}
       \mathcal{M}_n^{(s)}=\sum_{\alpha,\beta\in S_{n-2}}e_\alpha \tilde{e}_\beta m^{(0)}(\alpha|\beta)
    \end{equation*}
    and from the construcion of three type amplitudes, we can obtain
    \begin{equation*}
        {\cal M}^{(0)}_n\times{\cal M}^{(2)}_n={{\cal M}^{(1)}_n}^2
    \end{equation*}
    tree-level BCJ double copy relation.

\end{frame}
\section{Summary and Outlook}
\begin{frame}
    \frametitle{Summary}
    \begin{itemize}
        \item A compact form of tree-level S-matrix in 3 different theories are introduced
            \begin{equation*}
                \mathcal{M}_n^{(s)}=\sum_{\alpha,\beta\in S_{n-2}}e_\alpha e_\beta m^{(0)}(\alpha|\beta)
             \end{equation*}
        \item The computaion method for double partial amplitudes are given 
            \begin{equation*}
                    m_n^{(0)}(\alpha|\beta)=(-1)^{n-3+n_{\text{flip}}(\alpha|\beta)}\sum_{g\in\mathcal{T}(\alpha)\cap\mathcal{T}(\beta)}\prod_{e\in E(g)}\frac{1}{s_e}
            \end{equation*}
        \item The CK duality and BCJ double-copy relation can be easily obtained
            \begin{equation*}
                {\cal M}^{(0)}_n\times{\cal M}^{(2)}_n={{\cal M}^{(1)}_n}^2,\quad e_{g_t}=\pm(e_{g_s}-e_{g_u})
            \end{equation*}
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{The most general CHY form}
    In 2013, new formula for tree amplitudes of massless theories has been proposed by Cachazo, He and Yuan:
    \begin{equation*}
        \mathcal{A}=\boxed{\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)}\quad \mathcal{I}
    \end{equation*}
    \begin{itemize}
        \item Each particle is represented by a puncture in Riemann sphere.
        \item This form holds for general D-dimension.
        \item The boxed part is \alert{universial for all theories}.
        \item Only the integrand $\mathcal{I}$ determines the particular theory.
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{figure}[t]
        \centering
        \includegraphics[width=1\linewidth]{4.png}
    \end{figure}
    \alert{arxiv: 1412.3479}
\end{frame}
\begin{frame}
    \frametitle{Connection between other theories}
    \begin{figure}
        \centering
        \includegraphics[width=0.8\linewidth]{9.png}
    \end{figure}
\end{frame}

>>>>

\section{CHY Formula}
\begin{frame}
    \frametitle{Motivation}
    %Most of the developments of amplitudes before have made for some specific theories, like N=4 super yang-mills theory and N=8 supergravity.
    %The natural question is that what is the space of all field theories whose tree level S-matrix can be expressed in a compact form? 
    \begin{itemize}
        \item Compact form of amplitudes for sclar, pure Yang-Mills and gravity theories in any spacetime dimension.
        %The author introduce a compact form of tree level amplitudes for three different theories, colored scalar theory, pure Yang-Mills and Einstein gravity.
        %The concrete form of this formula implies that there is a relation between these three theories, and it may give some new insights of the connection between gravity and gauge theory.
        \item A special amplitude --- Double partial amplitude
        %Because of the special color structure of this scalar theory, the authors proposed a easy method to compute all scalar tree amplitudes, and then pure Yang-Mills and gravity can also be done using similar methods.
        \item BCJ double copy at tree level
        %In terms of this construction of amplitudes, it is easy to obtain the BCJ double copy relation.
        \item Many other theories are related, such as EYM, EM, NLSM and so on.
        %In the following paper of these authors, by introducing some special operations which performed on the integrand of CHY formula, they give some relations between other theories.   
        \item One-loop corrections to scattering amplitudes of scalars and gauge bosons can be obtained from tree amplitudes in one higher dimension. 
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{Scattering equations}
    % In the Witten-RSV formulation, tree-level field theory amplitudes are given as integrals that localize on generic spheres.
    It has been proposed that there is connection between the scattering data of n massless particles and the n-punctured sphere from a rational map
    \begin{equation*}
        k_\mu^a=\frac{1}{2\pi i}\oint_{|z-\sigma_a|}dz\frac{p^\mu(z)}{\prod ^n_{b=1}(z-\sigma_b)}
    \end{equation*}

    To discribe the n-punctured sphere more properly, we can introduce the Riemann sphere as
    \begin{equation*}
        \mathbb{CP}^1\cong \mathcal{S}^2\cong \mathbb{C}\cup\{\infty\}
    \end{equation*}
    all of the n punctured Riemann sphere actually compose a $\mathrm{n-3}$ dimension complex vector space $\mathfrak{m}_{0,n}$, 
    and $\sigma_a$ is a set of coordinates of this space.

@@

    %\begin{itemize}
    %    \item Third step, we can read off the corresponding amplitudes from the equivalent Feynman diagram. 
    %\end{itemize}
    %\begin{itemize}
    %\item First step, determine the orientation of the disk by ordering $\alpha$, and define the loop segments by ordering $\beta$, which also determine the orientation of every polygon.
    %    \item Second step, (1) each polygon with odd number vertices contributes a plus sign if the orientation is the same as disk, and a minus sign oppositely;
    %          (2) each polygon with even number vertices contribute a minus sign; (3) each intersection point contributes a minus sign.
    %\end{itemize}
    \begin{figure}
        \centering
        \includegraphics[width=1\linewidth]{6.png}
    \end{figure}
    The final answer is 
    \begin{equation*}
        m_8^{(0)}(I|54376218)=(-1)^6\left(\frac{1}{s_{21}}+\frac{1}{s_{18}}\right)\left(\frac{1}{s_{34}}+\frac{1}{s_{45}}\right)\frac{1}{s_{345}s_{812}s_{67}}
    \end{equation*}
\end{frame}
\begin{frame}
    Now we can unify the color factor and kinematic factor as e in all three theories, so the full amplitude can be written in a unified form
    \begin{equation*}
       \mathcal{M}_n^{(s)}=\sum_{\alpha,\beta\in S_{n-2}}e_\alpha \tilde{e}_\beta m^{(0)}(\alpha|\beta)
    \end{equation*}
    and from the construcion of three type amplitudes, we can obtain

    \begin{equation*}
        {\cal M}^{(0)}_n\times{\cal M}^{(2)}_n={{\cal M}^{(1)}_n}^2
    \end{equation*}
    tree-level BCJ double copy relation.

\end{frame}
\section{Summary and Outlook}
\begin{frame}
    \frametitle{Summary}
    \begin{itemize}
        \item A compact form of tree-level S-matrix in 3 different theories are introduced
            \begin{equation*}
                \mathcal{M}_n^{(s)}=\sum_{\alpha,\beta\in S_{n-2}}e_\alpha e_\beta m^{(0)}(\alpha|\beta)
             \end{equation*}
        \item The computaion method for double partial amplitudes are given 
            \begin{equation*}
                    m_n^{(0)}(\alpha|\beta)=(-1)^{n-3+n_{\text{flip}}(\alpha|\beta)}\sum_{g\in\mathcal{T}(\alpha)\cap\mathcal{T}(\beta)}\prod_{e\in E(g)}\frac{1}{s_e}
            \end{equation*}
        \item The Color-Kinematic duality and BCJ double-copy relation can be easily obtained
            \begin{equation*}
                {\cal M}^{(0)}_n\times{\cal M}^{(2)}_n={{\cal M}^{(1)}_n}^2
            \end{equation*}
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{The most general CHY form}
    In 2013, new formula for tree amplitudes of massless theories has been proposed by Cachazo, He and Yuan:
    \begin{equation*}
        \mathcal{A}=\boxed{\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)}\quad \mathcal{I}
    \end{equation*}
    \begin{itemize}
        \item Each particle is represented by a puncture in Riemann sphere.
        \item This form holds for general D-dimension.
        \item The boxed part is \alert{universial for all theories}.
        \item Only the integrand $\mathcal{I}$ determines the particular theory.
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{figure}[t]
        \centering
        \includegraphics[width=1\linewidth]{4.png}
    \end{figure}
    \alert{arxiv: 1412.3479}
\end{frame}
\begin{frame}
    \frametitle{Connection between other theories}
    \begin{figure}
        \centering
        \includegraphics[width=0.8\linewidth]{9.png}
    \end{figure}
\end{frame}
